Large-scale peer-to-peer network for mobile platforms: Challenges and Experiences\\

### 2019-02-10 paper.tex
Added initial related works draft

@@

\section{Related Work}
\label{sec:related}

\section{Conclusions and Future Work}
\label{sec:conclude}

>>>>

\begin{figure}[htbp]
\centerline{\includegraphics[width=\columnwidth]{figs/test_arch}}
\caption{Automated testing system for MNA}
\label{fig:test_arch}
\end{figure}

@@

%
\section{Related Work}
\label{sec:related}
%
Apart from the state-of-the-art cited earlier, there have been other
notable attempts at practical large-scale deployments and we describe
them here. Before mid-2000’s, most of the research on MANETs was based
on Department of Defense requirements, until commodity multi-hop ad
hoc networks began to be considered \cite{bruno-mesh-2005}. However,
it took another decade before wireless mesh networking was used
commercially to enable smartphones to connect via Bluetooth and WiFi
in a popular application called FireChat \cite{firechat}. The success
of FireChat, partially due to the news coverage of its use in
political situations in which governments restricted access to the
Internet, has led to many alternatives in the past few years. An
up-to-date list of such applications is available
here \footnote{https://alternativeto.net/software/firechat-by-open-garden/}
\section{Conclusions and Future Work}
\label{sec:conclude}
